### 2018-05-10 manuscript.rmd
added code for bayesian tree

>>>>

siphonophora_node_BI = ape::mrca( BIspeciestree )[ "Physalia physalis", "Agalma elegans" ]
cystonectae_node_BI = ape::mrca( BIspeciestree )[ "Physalia physalis", "Rhizophysa filiformis" ]
calycophora_node_BI = ape::mrca( BIspeciestree )[ "Kephyes ovata", "Craseoa lathetica" ]
euphysonectae_node_BI = ape::mrca( BIspeciestree )[ "Agalma elegans", "Undescribed sp L" ]

	support = as.numeric( BIspeciestree$node.label )
	support[ support > 99 ] = NA

	# pad tip values
	support = c( rep( NA, length( BIspeciestree$tip.label ) ), support )

	p_phylogram = ggtree( BIspeciestree ) +
      geom_text(aes(label=get_node_support(BIspeciestree, phylobayes_trees)), vjust=1.5, hjust=1, size=2.5, col="blue") +
			geom_tiplab( size=3 ) +
			xlim( 0, 12 ) +
			geom_cladelabel( node=cystonectae_node_BI, label="Cystonectae", align=FALSE, offset=1, color='red' ) +
			geom_cladelabel( node=calycophora_node_BI, label="Calycophora", align=FALSE, offset=1, color='blue' ) +
			geom_strip(
				which( species_tree$tip.label=="Agalma elegans" ),
				which( species_tree$tip.label=="Apolemia white" ),
				barsize=0.5,
				color='orange',
				offset=1,
				label='"Physonectae"'
			) +
			geom_strip(
				which( species_tree$tip.label=="Hydractinia symbiolongicarpus" ),
				which( species_tree$tip.label=="Nematostella vectensis" ),
				barsize=0.5,
				color='gray',
				offset=1,
				label='"Outgroups"'
			)

pdf("figures_raw/figure_S11_raw.pdf")
flip(p_phylogram, euphysonectae_node_BI, calycophora_node_BI)
dev.off()
